SMT-COMP 2023\\ 18th International Satisfiability Modulo Theory Competition

### 2023-07-06 2023/slides/presresults/input_for_certificates.tex
SMTCOMP presentation

@@

\MakeOnePage{Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}{s}{}

@@

\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{ALIA}{\sat,\uc}, \withtrack{AUFDTLIA}{\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{UFIDL}{\sat}, \withtrack{UFLIA}{\sat}}{s}{s}

@@

\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat,\fast}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}{s}{s}

@@

\MakeOnePage{Vampire}{}{\withtrack{Equality}{\fast}}{\withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{AUFLIRA}{\fast}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}}{}{s}

@@

\MakeOnePage{Yices2}{}{\withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}, \withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}}{\withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc}}{s}{s}

@@

\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}}{\withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_AUFLIA}{\uc}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_FP}{\sat}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{UFDT}{\fast}}{s}{s}

>>>>

\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{Bitvec}{\sat,\fast}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_ADT+BitVec}{\mv}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}}{\withtrack{ABVFP}{\sat,\fast}, \withtrack{ABVFPLRA}{\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}}{s}{s}

@@

\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc,\mv}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_LinearRealArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}}{\withtrack{LIA}{\sat,\fast}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_AUFLIA}{\uc,\mv}, \withtrack{QF\_AX}{\mv}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_FP}{\sat,\mv}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{UFDT}{\fast}, \withtrack{UFDTLIA}{\cloud}, \withtrack{UFNIA}{\cloud}}{s}{s}

@@

\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_ADT+LinArith}{\mv}, \withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral,\mv}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{ALIA}{\sat,\uc}, \withtrack{AUFDTLIA}{\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{UFIDL}{\sat}, \withtrack{UFLIA}{\sat}}{s}{s}

@@

@@

\MakeOnePage{Vampire}{\withtrack{Biggest Lead}{\cloud,\paralTrack}}{\withtrack{Arith}{\cloud,\paralTrack}, \withtrack{Equality}{\fast,\cloud,\paralTrack}, \withtrack{Equality+LinearArith}{\cloud,\paralTrack}, \withtrack{Equality+NonLinearArith}{\cloud,\paralTrack}}{\withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{AUFLIRA}{\fast}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}}{s}{s}

@@

\MakeOnePage{Yices2}{}{\withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}, \withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}}{\withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc,\mv}}{s}{s}

@@

\MakeOnePage{Z3-Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast,\mv}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat,\mv}}{\withtrack{QF\_IDL}{\unsat}}{s}{}

### 2023-07-06 2023/slides/presresults/slides.tex
SMTCOMP presentation

\documentclass[table]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{shapes,shapes.callouts,automata,trees}
\usetikzlibrary{decorations.pathmorphing,external,fit}
\usetikzlibrary{calc}
\usetikzlibrary{backgrounds} %used for the CEGAR figure
\usepackage{amssymb}
\usepackage{clrscode}
\usepackage{pifont}
\usepackage{pdfpages}
\geometry{papersize={16cm,9cm}}
%\tikzexternalize

@@

  \begin{frame}
    \frametitle{Other participants}
    \begin{itemize}
      \item Q3B
      \vitem SMT-RAT
      \vitem SMTS
      \vitem UltimateEliminatior+MathSAT
      \vitem Vampire
      \vitem Z3str4
    \end{itemize}
  \end{frame}

@@

  Submitted by organisers
  \begin{itemize}
  \item z3-4.8.17
  \item MathSAT 5.6.8
  \item Best solvers, per division, from previous years (23 Solvers)
  \end{itemize}
  \bigskip

  Submitted by participants
  \begin{itemize}
  \item Fixed solvers (OpenSMT, STP, Yices-ismt, Z3++,smtinterpol)
  \end{itemize}
\end{frame}

@@

  \bigskip
  Error scores:
  \begin{itemize}
  \item \emph{All Tracks}: given for sat reply for unsat instance, or vice versa
  \item \emph{Unsat Core}: given if returned core is satisfiable.
  \item \emph{Model Validation}: given if given model evaluates formula to \emph{false}
  \end{itemize}
  Error scores are draconian.
\end{frame}

@@

{
  \newcommand{\seq}{\texttt{;}}
  \newcommand{\paral}{\textbardbl}
  \newcommand{\sat}{$\top$}
  \newcommand{\unsat}{$\bot$}
  \newcommand{\fast}{\texttt{24}}
  \newcommand{\inc}{inc}
  \newcommand{\uc}{uc}
  \newcommand{\mv}{mv}
  \newcommand{\cloud}{cloud}
  \newcommand{\paralTrack}{parallel}
  %\newcommand{\all}{{\footnotesize (\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv)}}
  \newcommand{\withtrack}[2]{\textsc{#1}{{\footnotesize (#2)}}}

@@

  \begin{itemize}
  \item  111\,451 instances of 391\,363 have no status

@@

  \vitem We manually resolved the disagreements
  \begin{itemize}
    \item Authors confirmed solver unsoundness
    \item Sound solvers agreed on result
  \end{itemize}

  \vitem We had only ??? solvers with soundness issues: 
  \end{itemize}
\end{frame}

\begin{frame}{Plans for SMT-COMP 2022}
  \begin{itemize}
    \item Move to Dolmen as single model validator

      \vitem Dolmen worked well in QF\_FP (minor issue with empty output, simple
      to fix)
      \vitem pysmt timed out in two cases (locally with more time one of them
      succeeded)
      \vitem pysmt could not understand the model in 9 cases
      \vitem Dolmen is easy to extend to new theories
      \vitem Easy to integrate with correct-by-construction code extracted from
      Coq
      \vitem Should be more efficient for handling function call

\begin{frame}{Plans for SMT-COMP 2022}
  \begin{itemize}
    \item Proof \textit{validation} track

@@

\begin{frame}{SMT-COMP organizing committee}
  Three people organize the SMT-COMP.  In 2022:
  \begin{itemize}
  \item Haniel Barbosa
  \item Jochen Hoenicke
  \item Fran\c{c}ois Bobot
  \end{itemize}

  Both Haniel and Jochen have been organizers for three-years. One of them
  should be replaced.
  \bigskip

@@

\begin{frame}{Acknowledgements}
  \begin{itemize}
    \item \emph{Andrea Micheli}: pysmt
    \item \emph{Guillaume Bury}: Model Validator
    \item \emph{Clark Barrett, Pascal Fontaine, Aina Niemetz, Mathias Preiner, Hans-Jörg Schurr}: SMT-LIB benchmarks
    \item \emph{Aaron Stump}: StarExec support
    \item \emph{Mike Whalen and team}: Cloud/Parallel Track
  \end{itemize}
  \bigskip

@@

\begin{frame}[shrink=0.95]{Benchmark contributors}
  In 2022 \emph{new benchmarks} were contributed by:

>>>>

\documentclass[table]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{shapes,shapes.callouts,automata,trees}
\usetikzlibrary{decorations.pathmorphing,external,fit}
\usetikzlibrary{calc}
\usetikzlibrary{backgrounds} %used for the CEGAR figure
\usepackage{amssymb}
\usepackage{clrscode}
\usepackage{pifont}
\usepackage{pdfpages}
\geometry{papersize={16cm,9cm}}
%\tikzexternalize
\usepackage{multicol}

@@

\newcommand{\myvideopdf}[2]{
\begin{frame}
  \frametitle{#1}
  \begin{center}
    video: \texttt{#2}    
  \end{center}
\end{frame}
}

\myincludepdf{slides-bitwuzla.pdf}

\myincludepdf{slides-colibri.pdf}

\myvideopdf{cvc5-NRA-LS}{slides-cvc5-nra-ls.mp4}

\myvideopdf{iProver}{slides-iProver.mp4}

\myvideopdf{ismt, Yices-ismt}{slides-ismt.mp4}

\myincludepdf{slides-ismt-ppt.pdf}

\myincludepdf{slides-opensmt.pdf}

\myvideopdf{Ostrich}{slides-Ostrich.mkv}

\myincludepdf{slides-smtinterpol.pdf}

\myincludepdf{slides-smtrat.pdf}

\myvideopdf{UltimateEliminator+MathSAT}{slides-UltimateEliminator.mkv}

\myincludepdf{slides-vampire.pdf}

\myincludepdf{slides-yaga.pdf}

\myincludepdf{slides-Yices-2023.pdf}

\myincludepdf{slides-YicesQS-2023.pdf}

%\myvideopdf{Z3-Z3++}{slides-z3-z3++.mp4}
\begin{frame}
  \frametitle{Z3-Z3++}

  \begin{center}
    \url{https://youtu.be/fBB0Wxxf9vA}
  \end{center}
\end{frame}

  \begin{frame}
    \frametitle{Other participants}
    \begin{itemize}
\item cvc5
\vitem Q3B
\vitem Q3B-pBDD
\vitem STP
\vitem UltimateIntBlastingWrapper+SMTInterpol
\vitem z3-alpha
\vitem Z3-Noodler
\vitem Z3-Owl
    \end{itemize}
  \end{frame}

@@

  Submitted by organisers
  \begin{itemize}
  \item Best solvers, per division, from previous years (27 Solvers)
  \end{itemize}
  \bigskip

  Submitted by participants
  \begin{itemize}
  \item Fixed solvers (OSTRICH, Z3-Owl, Bitwuzla, Yices2, Z3-Noodler, iProver)  
  \end{itemize}
\end{frame}

@@

  \bigskip
  Error scores:
  \begin{itemize}
  \item \emph{All Tracks}: given for sat reply for unsat instance, or vice versa
  \item \emph{Unsat Core}: given if returned core is satisfiable.
  \item \emph{Model Validation}: given if given model evaluates formula to \emph{false}
  \end{itemize}
  Error scores are \textbf{draconian}.
\end{frame}

@@

\newcommand{\seq}{\texttt{;}}
\newcommand{\paral}{\textbardbl}
\newcommand{\sat}{$\top$}
\newcommand{\unsat}{$\bot$}
\newcommand{\fast}{\texttt{24}}
\newcommand{\inc}{inc}
\newcommand{\uc}{uc}
\newcommand{\mv}{mv}
\newcommand{\cloud}{cloud}
\newcommand{\paralTrack}{parallel}

\begin{frame}
  \frametitle{Results}
  \begin{center}
    \begin{tabular}{|cl|cl|}
  \hline
  \sat & satisfiable & \unsat & unsatisfiable \\
  \seq & sequential & \paral & parallel \\
  \fast & less than 24s & \inc & incremental \\
  \uc & unsat core & \mv & model validation \\
  \hline
\end{tabular}
\end{center}
\vfill
Experimental track are added in the slides but are not present
in the certificates
\end{frame}

{
  %\newcommand{\all}{{\footnotesize (\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv)}}
  \newcommand{\withtrack}[2]{\textsc{#1}{{\footnotesize (#2)}}}

@@

  \begin{itemize}
  \item  50411 benchmarks of 227\,938 have no status

@@

  \vitem We manually resolved the disagreements: authors confirmed solver
  unsoundness
  \vitem We had 10 solvers with soundness issues:
  \begin{columns}
    \column{0.45\textwidth}
    \begin{itemize}
      \item Bitwuzla (uc printing error)
      \item iProver (\& Fixed)
      \item OSTRICH
      \item Q3B
      \item UltimateEliminator+MathSAT
    \end{itemize} 
    \column{0.55\textwidth}
    \begin{itemize}
      \item UltimateIntBlastingWrapper+SMTInterpol
      \item Vampire
      \item Yices2 (\& Fixed)
      \item Z3-Noodler (\& Fixed)
      \item Z3-Owl (\& Fixed)
    \end{itemize} 
\end{columns}

  \end{itemize}
  \end{frame}

\begin{frame}{Plans for SMT-COMP 2023}
  \begin{itemize}
    \item "Revelations are found in clouds” --- Serge King
    \item MV: Algebraic number non experimental
    \item MV: partial function more discussion needed
    \item MV: array theory more discussion needed
  \end{itemize}
\end{frame}

\begin{frame}{Plans for SMT-COMP 2023?}
  \begin{itemize}
    \item Proof \textit{validation} track

@@

\begin{frame}{SMT-COMP organizing committee}
  Three people organize the SMT-COMP.  In 2023:
  \begin{itemize}
  \item Martin Bromberger
  \item Jochen Hoenicke
  \item Fran\c{c}ois Bobot
  \end{itemize}

  Jochen have been organizer for four-years! He can rest happy.
  \bigskip

@@

\begin{frame}{Acknowledgements}
  \begin{itemize}
    \item \emph{Andrea Micheli}: pysmt
    \item \emph{Guillaume Bury, FB.}: Model Validator
    \item \emph{Clark Barrett, Pascal Fontaine, Aina Niemetz, Mathias Preiner, Hans-Jörg Schurr}: SMT-LIB benchmarks
    \item \emph{Aaron Stump}: StarExec support
    \item \emph{Mike Whalen and team}: Cloud/Parallel Track
  \end{itemize}
  \bigskip

@@

\begin{frame}[shrink=0.95]{Benchmark contributors}
  In 2023 \emph{new benchmarks} were contributed by:
